---
title: "AccuracyDist_1"
author: "Olga Alieva"
date: "2022-12-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Load packages
```{r message=FALSE}
library(tidyverse)
library(yardstick)
library(stringr)
```

# Load data
```{r}
load("/Users/olga/R_Workflow/compareDist/data/CanbNS.Rdata")
load("/Users/olga/R_Workflow/compareDist/data/CanbS.Rdata")
load("/Users/olga/R_Workflow/compareDist/data/ClarNS.Rdata")
load("/Users/olga/R_Workflow/compareDist/data/ClarS.Rdata")
load("/Users/olga/R_Workflow/compareDist/data/CosNS.Rdata")
load("/Users/olga/R_Workflow/compareDist/data/CosS.Rdata")
load("/Users/olga/R_Workflow/compareDist/data/EuclNS.Rdata")
load("/Users/olga/R_Workflow/compareDist/data/EuclS.Rdata")
load("/Users/olga/R_Workflow/compareDist/data/JeffNS.Rdata")
load("/Users/olga/R_Workflow/compareDist/data/Labbe.Rdata")
load("/Users/olga/R_Workflow/compareDist/data/ManhNS.Rdata")
load("/Users/olga/R_Workflow/compareDist/data/ManhS.Rdata")
load("/Users/olga/R_Workflow/compareDist/data/TanNS.Rdata")
load("/Users/olga/R_Workflow/compareDist/data/TanS.Rdata")
```

# Bind data
```{r}
data_w <- manh_s %>% 
  bind_rows(manh_ns) %>% 
  bind_rows(eucl_ns) %>% 
  bind_rows(eucl_s) %>% 
  bind_rows(cos_ns) %>% 
  bind_rows(cos_s) %>% 
  bind_rows(tan_ns) %>% 
  bind_rows(tan_s) %>% 
  bind_rows(canb_ns) %>% 
  bind_rows(canb_s) %>% 
  bind_rows(clar_ns) %>% 
  bind_rows(clar_s) %>% 
  bind_rows(jeff_ns) %>% 
  bind_rows(labbe) 
```

# Get mean accuracy for each method
```{r}
acc_all_w <- data_w %>% 
  mutate(expected = as.factor(expected)) %>% 
  mutate(predicted = as.factor(predicted)) %>% 
  group_by(method, scale) %>% 
  accuracy(truth = expected, estimate = predicted) %>% 
  select(-.metric, -.estimator) %>% 
  arrange(-.estimate) %>% 
  mutate(.estimate = round(.estimate, 3))
# write_csv(acc_all_w, "tables/AccAllW.csv")
```

## Compare Acc W and C
```{r}
dw <- acc_all_w %>% 
  mutate(type = rep("word", nrow(acc_all_w))) 

dc <- acc_all_c %>% 
  mutate(type = rep("char", nrow(acc_all_w))) 

dw %>% 
  bind_rows(dc) %>% 
  unite(method, method, scale, sep = "_") %>% 
  mutate(method = gsub("ALSE", "", method)) %>% 
  mutate(method = gsub("RUE", "", method)) %>% 
  filter(.estimate > 0.5) %>% 
  mutate(method = reorder(method, .estimate)) %>% 
  ggplot(aes(method, .estimate, fill = as.factor(type))) +
  geom_bar(position = "dodge", stat = "identity",
           show.legend = F) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
  
```

# save bar plot

```{r}
ggsave(
  filename = "images/BarPlot.png",
  plot = last_plot(),
  device = "png",
  scale = 1,
  width = NA,
  height = 900,
  units = "px",
  dpi = 300
)
```

# Delete methods with very low performace
```{r}
data_w <- manh_s %>% 
  bind_rows(manh_ns) %>% 
  bind_rows(eucl_ns) %>% 
  bind_rows(cos_ns) %>% 
  bind_rows(cos_s) %>% 
  bind_rows(tan_ns) %>% 
  bind_rows(canb_ns) %>% 
  bind_rows(clar_ns) %>% 
  bind_rows(jeff_ns) %>% 
  bind_rows(labbe)
```


# Accuracy by mfw / sample size
```{r}
data_w %>% 
  mutate(mfw = cut(mfw, breaks=c(0, 200, 400, 600, 800, 1000), 
                   labels=paste0("mfw", c(200, 400, 600, 800, 1000),
                                 sep=""))) %>% 
  group_by(size, mfw, method, scale) %>%
  mutate(expected = as.factor(expected)) %>% 
  mutate(predicted = as.factor(predicted)) %>% 
  accuracy(truth = expected, estimate = predicted) %>% 
  ggplot(aes(x = size, y=.estimate, color = mfw)) +
  geom_line() + 
  theme(legend.position = c(0.8, 0.2)) +
  facet_wrap(facets = ~method + scale, nrow = 2) +
  theme_bw() + 
  xlab("длина отрывка") +
  ylab("точность")
```

## Save plot

```{r}
ggsave(
  filename = "images/AccW.png",
  plot = last_plot(),
  device = "png",
  scale = 1,
  width = NA,
  height = 1200,
  units = "px",
  dpi = 300
)
```

# Maximum accuracy 
```{r}
top_w <- data_w %>% 
  group_by(method, scale, mfw, size, id) %>%
  mutate(expected = as.factor(expected)) %>% 
  mutate(predicted = as.factor(predicted)) %>%
  accuracy(truth = expected, estimate = predicted) %>% 
  select(-.metric, -.estimator) %>% 
  group_by(method, scale, mfw, size) %>% 
  summarise(mean = mean(.estimate)) %>% 
  mutate(mean = round(mean, 3)) %>% 
  ungroup() %>% 
  top_n(wt = mean, n=30) %>% 
  arrange(-mean)
# write_csv(top_w, "tables/TopW.csv")
```

# Max accuracy for short text
```{r}
short <- data_w %>% 
  filter(size %in% c(1000, 1500, 2000)) %>% 
  group_by(method, scale, mfw, size) %>%
  mutate(expected = as.factor(expected)) %>% 
  mutate(predicted = as.factor(predicted)) %>%
  accuracy(truth = expected, estimate = predicted) %>% 
  select(-.metric, -.estimator) 

top_short <- short %>%
  group_by(size) %>% 
  slice_max(n = 3, with_ties = F, order_by = .estimate) %>% 
  mutate(.estimate = round(.estimate, 3))
```

# Standard Deviation - New

```{r}
short_new <- data_w %>% 
  filter(size %in% c(1000, 1500, 2000)) %>% 
  group_by(method, scale, mfw, size, id) %>%
  mutate(expected = as.factor(expected)) %>% 
  mutate(predicted = as.factor(predicted)) %>%
  accuracy(truth = expected, estimate = predicted) %>% 
  select(-.metric, -.estimator) %>% 
  ungroup

short_sd <- short_new %>%
  group_by(method, scale, mfw, size) %>% 
  summarise(.sd = sd(.estimate)) %>% 
  mutate(.sd = round(.sd, 3))
```

## Join Sd and Mean

```{r}
top_short_sd <- top_short %>% left_join(short_sd)
# write_csv(top_short_sd, "tables/TopShortW.csv")
```

## How accuracy is distributed?

```{r}
plot_data <- top_short_sd %>% 
  select(-.estimate, -.sd) %>% 
  inner_join(short_new) %>% 
  unite(method, method, scale, mfw, size, sep = "_" ) %>% 
  mutate(method = gsub("ALSE", "", method)) %>% 
  mutate(method = gsub("RUE", "", method))

plot_data %>% 
  ggplot(aes(.estimate)) + 
  geom_line(aes(color=method), stat = "density", size = 1.1, alpha = 0.7) + 
  theme_bw()

ggsave(
  filename = "images/DensityAccW.png",
  plot = last_plot(),
  device = "png",
  scale = 1,
  width = NA,
  height = NA,
  units = "px",
  dpi = 300
)
```

# Where classifiers fail
```{r}
data_w %>% filter(method == "cosine", scale == T) %>% 
  mutate(expected = as.factor(expected)) %>% 
  mutate(predicted = as.factor(predicted)) %>%
  group_by(expected) %>% 
  accuracy(truth = expected, estimate = predicted) %>% 
  select(-.metric, -.estimator) %>% 
  arrange(.estimate)

data_w %>% filter(method == "labbe") %>% 
  mutate(expected = as.factor(expected)) %>% 
  mutate(predicted = as.factor(predicted)) %>%
  group_by(expected) %>% 
  accuracy(truth = expected, estimate = predicted) %>% 
  select(-.metric, -.estimator) %>% 
  arrange(.estimate)

data_w %>% filter(method == "tanimoto", scale == F) %>% 
  mutate(expected = as.factor(expected)) %>% 
  mutate(predicted = as.factor(predicted)) %>%
  group_by(expected) %>% 
  accuracy(truth = expected, estimate = predicted) %>% 
  select(-.metric, -.estimator) %>% 
  arrange(.estimate)
```

# Common errors
```{r}
errors <- data_w %>% filter(method == "cosine", scale == T,
                  expected %in% c("Aristotle", "Aristides", 
                                  "Demosthenes")) %>%
  group_by(expected) %>% 
  count(predicted) %>% ungroup() %>% 
  group_by(expected) %>% 
  slice_max(n, n = 4)
  
write_csv(errors, "Errors3W.csv")
```

# Where classifiers perform best
```{r}
data_w %>% filter(method == "cosine", scale == T) %>% 
  mutate(expected = as.factor(expected)) %>% 
  mutate(predicted = as.factor(predicted)) %>%
  group_by(expected) %>% 
  accuracy(truth = expected, estimate = predicted) %>% 
  select(-.metric, -.estimator) %>% 
  arrange(-.estimate)

data_w %>% filter(method == "labbe") %>% 
  mutate(expected = as.factor(expected)) %>% 
  mutate(predicted = as.factor(predicted)) %>%
  group_by(expected) %>% 
  accuracy(truth = expected, estimate = predicted) %>% 
  select(-.metric, -.estimator) %>% 
  arrange(-.estimate)

data_w %>% filter(method == "tanimoto", scale == F) %>%
  mutate(expected = as.factor(expected)) %>% 
  mutate(predicted = as.factor(predicted)) %>%
  group_by(expected) %>% 
  accuracy(truth = expected, estimate = predicted) %>% 
  select(-.metric, -.estimator) %>% 
  arrange(-.estimate)
```



