---
title: "CompareDist_2"
author: "Olga Alieva"
date: "2022-12-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Отличается от CompareDist1 только тем, что те же тесты на энграммах, а не на словах**

# load packages and source functions
```{r message=FALSE}
library(tidyverse)
library(stylo)
library(philentropy)
source("~/R_Workflow/compareDist/DistResample.R")
```

# Sample size and number of features
```{r}
# sample size and number of features
sample.size = seq(1000, 7000, 500)
nr.features = seq(100, 1000, 100)
```

# Load corpus
```{r message=FALSE}
# load corpus
input.texts <-  load.corpus.and.parse(files = "all", 
                                      corpus.dir = "corpus", 
                                      features = "c", 
                                      ngram.size = 3) 
```


# 1 Manhattan, not scaled 
```{r}
set.seed(1234)
manh3N_ns <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="manhattan",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T, 
                                         use.scaled.freq = F),
                           .id = "id")
    manh3N_ns <- bind_rows(manh3N_ns, iter)
  }
}
save(manh3N_ns, file = "data/3NManhNS.Rdata")
```

# Manhattan, scaled 
```{r}
set.seed(1234)
manh3N_s <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="manhattan",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T,
                                         use.scaled.freq = T),
                           .id = "id")
    manh3N_s <- bind_rows(manh3N_s, iter)
  }
}
save(manh3N_s, file = "data/3NManhS.Rdata")
```

# Euclidean, not scaled
```{r}
set.seed(1234)
eucl3N_ns <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="euclidean",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T, 
                                         use.scaled.freq = F),
                           .id = "id")
    eucl3N_ns <- bind_rows(eucl3N_ns, iter)
  }
}
save(eucl3N_ns, file = "data/3NEuclNS.Rdata")
```

# Euclidean, scaled
```{r}
set.seed(1234)
eucl3N_s <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="euclidean",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T, 
                                         use.scaled.freq = T),
                           .id = "id")
    eucl3N_s <- bind_rows(eucl3N_s, iter)
  }
}
save(eucl3N_s, file = "data/3NEuclS.Rdata")
```

# Cosine, not scaled
```{r}
set.seed(1234)
cos3N_ns <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="cosine",
                                         nr.features = i,
                                         direction = "max",
                                         relative = T, 
                                         use.scaled.freq = F),
                           .id = "id")
    cos3N_ns <- bind_rows(cos3N_ns, iter)
  }
}
save(cos3N_ns, file = "data/3NCosNS.Rdata")
```

# Cosine, scaled
```{r}
set.seed(1234)
cos3N_s <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="cosine",
                                         nr.features = i,
                                         direction = "max",
                                         relative = T,
                                         use.scaled.freq = T),
                           .id = "id")
    cos3N_s <- bind_rows(cos3N_s, iter)
  }
}
save(cos3N_s, file = "data/3NCosS.Rdata")
```

# Canberra, not scaled
```{r}
set.seed(1234)
canb3N_ns <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="canberra",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T, 
                                         use.scaled.freq = F),
                           .id = "id")
    canb3N_ns <- bind_rows(canb3N_ns, iter)
  }
}
save(canb3N_ns, file = "data/3NCanbNS.Rdata")
```

# Canberra, scaled
```{r}
set.seed(1234)
canb3N_s <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="canberra",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T, 
                                         use.scaled.freq = T),
                           .id = "id")
    canb3N_s <- bind_rows(canb3N_s, iter)
  }
}
save(canb3N_s, file = "data/3NCanbS.Rdata")
```

# Tanimoto, not scaled
```{r}
set.seed(1234)
tan3N_ns <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="tanimoto",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T, 
                                         use.scaled.freq = F),
                           .id = "id")
    tan3N_ns <- bind_rows(tan3N_ns, iter)
  }
}
save(tan3N_ns, file = "data/3NTanNS.Rdata")
```

# Tanimoto, scaled
```{r}
set.seed(1234)
tan3N_s <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="tanimoto",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T, 
                                         use.scaled.freq = T),
                           .id = "id")
    tan3N_s <- bind_rows(tan3N_s, iter)
  }
}
save(tan3N_s, file = "data/3NTanS.Rdata")
```

# Clark, not scaled
```{r}
set.seed(1234)
clar3N_ns <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="clark",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T, 
                                         use.scaled.freq = F),
                           .id = "id")
    clar3N_ns <- bind_rows(clar3N_ns, iter)
  }
}
save(clar3N_ns, file = "data/3NClarNS.Rdata")
```

# Clark,  scaled
```{r}
set.seed(1234)
clar3N_s <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="clark",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T, 
                                         use.scaled.freq = T),
                           .id = "id")
    clar3N_s <- bind_rows(clar3N_s, iter)
  }
}
save(clar3N_s, file = "data/3NClarS.Rdata")
```

# Jeffreys, not scaled
```{r}
set.seed(1234)
jeff3N_ns <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="jeffreys",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T, 
                                         use.scaled.freq = F),
                           .id = "id")
    jeff3N_ns <- bind_rows(jeff3N_ns, iter)
  }
}
save(jeff3N_ns, file = "data/3NJeffNS.Rdata")
```

# Labbe 
```{r}
set.seed(1234)
labbe3N <- tibble()
for(n in sample.size){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="labbe",
                                         nr.features = NULL,
                                         direction = "min",
                                         relative = F, 
                                         use.scaled.freq = F),
                           .id = "id")
    labbe3N <- bind_rows(labbe3N, iter)
}
save(labbe3N, file = "data/3NLabbe.Rdata")
```

