---
title: "compareDist_1"
author: "Olga Alieva"
date: "2022-12-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages and source functions
```{r message=FALSE}
library(tidyverse)
library(stylo)
library(philentropy)
source("~/R_Workflow/compareDist/DistResample.R")
source("~/R_Workflow/compareDist/GetPred.R")
```

# Sample size and number of features
```{r}
# sample size and number of features
sample.size = seq(1000, 7000, 500)
nr.features = seq(100, 1000, 100)
```

# Load corpus
```{r message=FALSE}
# load corpus
input.texts <-  load.corpus.and.parse(files = "all", 
                                      corpus.dir = "corpus", 
                                      features = "w", 
                                      ngram.size = 1) 
```

# One preliminary test on the whole corpus 
```{r message=FALSE}
set.seed(1234)
sp <- size.penalize(mfw = seq(100, 1000, 100), features = wordlist, 
              corpus.dir = "corpus",
              sample.size.coverage = seq(1000, 7000, 500),
              sample.with.replacement = T,
              iterations = 10, classification.method = "delta",
              list.cutoff = 1000)

```

# Calculate accuracy
```{r}
acc <- c()
for(i in 1:length(sp$accuracy.scores)){
  cm <- sp$accuracy.scores[[i]]
  a <- sum(rowSums(cm)) / (nrow(cm) * ncol(cm))
  acc <- c(acc, a)
}
mean(acc) # 0.85
```

# 1 Manhattan, not scaled 
```{r}
set.seed(1234)
manh_ns <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="manhattan",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T, 
                                         use.scaled.freq = F),
                           .id = "id")
    manh_ns <- bind_rows(manh_ns, iter)
  }
}
save(manh_ns, file = "data/ManhNS.Rdata") 
```

# Manhattan, scaled 
```{r}
set.seed(1234)
manh_s <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="manhattan",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T,
                                         use.scaled.freq = T),
                           .id = "id")
    manh_s <- bind_rows(manh_s, iter)
  }
}
save(manh_s, file = "data/ManhS.Rdata")
```

# Euclidean, not scaled
```{r}
set.seed(1234)
eucl_ns <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="euclidean",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T, 
                                         use.scaled.freq = F),
                           .id = "id")
    eucl_ns <- bind_rows(eucl_ns, iter)
  }
}
save(eucl_ns, file = "data/EuclNS.Rdata")
```

# Euclidean, scaled
```{r}
set.seed(1234)
eucl_s <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="euclidean",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T, 
                                         use.scaled.freq = T),
                           .id = "id")
    eucl_s <- bind_rows(eucl_s, iter)
  }
}
save(eucl_s, file = "data/EuclS.Rdata")
```

# Cosine, not scaled
```{r}
set.seed(1234)
cos_ns <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="cosine",
                                         nr.features = i,
                                         direction = "max",
                                         relative = T, 
                                         use.scaled.freq = F),
                           .id = "id")
    cos_ns <- bind_rows(cos_ns, iter)
  }
}
save(cos_ns, file = "data/CosNS.Rdata")
```

# Cosine, scaled
```{r}
set.seed(1234)
cos_s <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="cosine",
                                         nr.features = i,
                                         direction = "max",
                                         relative = T,
                                         use.scaled.freq = T),
                           .id = "id")
    cos_s <- bind_rows(cos_s, iter)
  }
}
save(cos_s, file = "data/CosS.Rdata")
```

# Canberra, not scaled
```{r}
set.seed(1234)
canb_ns <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="canberra",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T, 
                                         use.scaled.freq = F),
                           .id = "id")
    canb_ns <- bind_rows(canb_ns, iter)
  }
}
save(canb_ns, file = "data/CanbNS.Rdata")
```

# Canberra, scaled
```{r}
set.seed(1234)
canb_s <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="canberra",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T, 
                                         use.scaled.freq = T),
                           .id = "id")
    canb_s <- bind_rows(canb_s, iter)
  }
}
save(canb_s, file = "data/CanbS.Rdata")
```

# Tanimoto, not scaled
```{r}
set.seed(1234)
tan_ns <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="tanimoto",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T, 
                                         use.scaled.freq = F),
                           .id = "id")
    tan_ns <- bind_rows(tan_ns, iter)
  }
}
save(tan_ns, file = "data/TanNS.Rdata")
```

# Tanimoto, scaled
```{r}
set.seed(1234)
tan_s <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="tanimoto",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T, 
                                         use.scaled.freq = T),
                           .id = "id")
    tan_s <- bind_rows(tan_s, iter)
  }
}
save(tan_s, file = "data/TanS.Rdata")
```

# Clark, not scaled
```{r}
set.seed(1234)
clar_ns <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="clark",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T, 
                                         use.scaled.freq = F),
                           .id = "id")
    clar_ns <- bind_rows(clar_ns, iter)
  }
}
save(clar_ns, file = "data/ClarNS.Rdata")
```

# Clark,  scaled
```{r}
set.seed(1234)
clar_s <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="clark",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T, 
                                         use.scaled.freq = T),
                           .id = "id")
    clar_s <- bind_rows(clar_s, iter)
  }
}
save(clar_s, file = "data/ClarS.Rdata")
```

# Jeffreys, not scaled
```{r}
set.seed(1234)
jeff_ns <- tibble()
for(n in sample.size){
  for(i in nr.features){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="jeffreys",
                                         nr.features = i,
                                         direction = "min",
                                         relative = T, 
                                         use.scaled.freq = F),
                           .id = "id")
    jeff_ns <- bind_rows(jeff_ns, iter)
  }
}
save(jeff_ns, file = "data/JeffNS.Rdata")
```

# Labbe 
```{r}
set.seed(1234)
labbe <- tibble()
for(n in sample.size){
    iter <- map_dfr(1:10, ~dist.resample(sample.size=n,
                                         method="labbe",
                                         nr.features = NULL,
                                         direction = "min",
                                         relative = F, 
                                         use.scaled.freq = F),
                           .id = "id")
    labbe <- bind_rows(labbe, iter)
}
save(labbe, file = "data/Labbe.Rdata")
```
